Formula 1 2022 Regulation Changes

### 2024-04-20 paper/paper.qmd
added verstappen, hamilton, leclerc jeddah quali speed comparison graphs

@@

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-circuits
#| tbl-cap: F1 Circuits Analysis
library(tidyverse)
library(kableExtra)

variable_data <- data.frame( 
  Circuit_Name = c("Saudi Arabia", 
               "Netherlands"), 
  Track_Type = c("Top Speed",
                  "High Downforce"), 
  Tyre_Wear = c("High", 
              "Low")
)
variable_data |>
 slice(1:10) |>
  kable(digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

@@

```{r}
#| label: fig-overtakes
#| fig-cap: Number of Overtakes 2021 v 2022
#| echo: false
#| warning: false
#| message: false

data <- read.csv("../data/raw_data/Overtaking_Season_Averages.csv")

# Filter data for the years 2021 and 2022
filtered_data <- data[data$Season %in% c(2021, 2022), ]

ggplot(filtered_data, aes(x = as.factor(Season), y = Overtakes, fill = "Total Overtakes")) +
    geom_bar(stat = "identity", color = "black", fill = "blue") +
    labs(title = "Total Overtakes (2021-2022)",
         x = "Season", y = "Number of Overtakes") +
    theme_minimal()
```

```{r}
#| label: fig-overtakes
#| fig-cap: Number of Overtakes Seen on TV 2021 v 2022
#| echo: false
#| warning: false
#| message: false

data <- read.csv("../data/raw_data/Overtaking_Season_Averages.csv")

# Filter data for the years 2021 and 2022
filtered_data <- data[data$Season %in% c(2021, 2022), ]

ggplot(filtered_data, aes(x = as.factor(Season), y = Overtakes.on.TV, fill = "Overtakes on TV")) +
    geom_bar(stat = "identity", color = "black", fill = "red") +
    labs(title = "Overtakes on TV (2021-2022)",
         x = "Season", y = "Number of Overtakes on TV") +
    theme_minimal()
```

```{r}
#| label: fig-verspeed-jeddah
#| fig-cap: Verstappen Speed Comparison - Qualifying Jeddah 2022 vs 2021
#| echo: false
#| warning: false
#| message: false

ver_telemetry_data_jeddah_2022 <- read.csv("../data/raw_data/verstappen_telemetry_jeddah.csv")
ver_telemetry_data_jeddah_2021 <- read.csv("../data/raw_data/verstappen_telemetry_jeddah_2021.csv")

# Assuming telemetry_data_2022 and telemetry_data_2021 are your datasets
ver_telemetry_data_jeddah_2022$season <- "2022"
ver_telemetry_data_jeddah_2021$season <- "2021"

# Combine the datasets
combined_data <- rbind(ver_telemetry_data_jeddah_2022, ver_telemetry_data_jeddah_2021)

# Convert session_time to a numeric type if not already
combined_data$session_time <- as.numeric(combined_data$session_time)

# Plotting
ggplot(combined_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "blue"))

```{r}
#| label: fig-hamspeed-jeddah
#| fig-cap: Hamilton Speed Comparison - Qualifying Jeddah 2022 vs 2021
#| echo: false
#| warning: false
#| message: false

ham_telemetry_data_jeddah_2022 <- read.csv("../data/raw_data/hamilton_telemetry_jeddah.csv")
ham_telemetry_data_jeddah_2021 <- read.csv("../data/raw_data/hamilton_telemetry_jeddah_2021.csv")

# Assuming telemetry_data_2022 and telemetry_data_2021 are your datasets
ham_telemetry_data_jeddah_2022$season <- "2022"
ham_telemetry_data_jeddah_2021$season <- "2021"

# Combine the datasets
combined_data <- rbind(ham_telemetry_data_jeddah_2022, ham_telemetry_data_jeddah_2021)

# Convert session_time to a numeric type if not already
combined_data$session_time <- as.numeric(combined_data$session_time)

# Plotting
ggplot(combined_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "purple", "2022" = "gold"))
```
```{r}
#| label: fig-lecspeed-jeddah
#| fig-cap: Leclerc Speed Comparison - Qualifying Jeddah 2022 vs 2021
#| echo: false
#| warning: false
#| message: false

lec_telemetry_data_jeddah_2022 <- read.csv("../data/raw_data/leclerc_telemetry_jeddah.csv")
lec_telemetry_data_jeddah_2021 <- read.csv("../data/raw_data/leclerc_telemetry_jeddah_2021.csv")

# Assuming telemetry_data_2022 and telemetry_data_2021 are your datasets
lec_telemetry_data_jeddah_2022$season <- "2022"
lec_telemetry_data_jeddah_2021$season <- "2021"

# Combine the datasets
combined_data <- rbind(lec_telemetry_data_jeddah_2022, lec_telemetry_data_jeddah_2021)

# Convert session_time to a numeric type if not already
combined_data$session_time <- as.numeric(combined_data$session_time)

# Plotting
ggplot(combined_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "darkgreen"))
```
